Teaching

### 2025-01-06 posts/SP2 Review Response/ReviewResponse.qmd

| 3   | The implications from your findings are also not clear. The current results show reduced smartphone use when engaging high "core-number" contacts. Does this suggest that one should have more interactions with such contacts to minimize their screen time? But the effect seems to be muted for the heaviest smartphone users, meaning this strategy wouldn't be effective for those who might be really addicted.                                                                                                                                                                                            | We identified smartphone users who are addicted to smartphone. To the best of knowledge, there is no quantitative definition of smartphone addiction. We define smartphone addiction based on multiple criterias:                                                                                                                                                                                                                                                                                         |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 1.  Observations with daily screen time that are greater than 5 hours (300 minutes).                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 2.  Observations with daily screen time that are ranked top 10%, 20%, 30% among population.                                                                                                                                                                                                                                                                                                                                                                                                               |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 3.  Top 10 % screen time observations for each individuals' observations.                                                                                                                                                                                                                                                                                                                                                                                                                                 |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | We then estimated the probability of addiction with a logit model:                                                                                                                                                                                                                                                                                                                                                                                                                                        |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | $\begin{align} \ln \left(\frac{\operatorname{Pr}\left(\text { Addiction }_{i t}=1 \mid \boldsymbol{X}_{i t}\right)}{1-\operatorname{Pr}\left(\text { Addiction }_{i t}=1 \mid \boldsymbol{X}_{i t}\right)}\right) &= \nonumber \\ &\quad \beta_{0} + \beta_{1} \cdot \text{Social Network Features}_{it} \nonumber \\ &\quad+ \alpha \cdot X_{it} + \theta_{i} +\lambda_{t} + \varepsilon_{it}\end{align}$                                                                                                |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | All estimation results show that the increase in core number is associated with a decrease in the likelihood of smartphone addiction. For example:                                                                                                                                                                                                                                                                                                                                                        |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | ![](images/clipboard-2847711747.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 4   | Does a single interaction by call/text suffice to trigger this effect?                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           | **In the first version of this paper, the activation threshold is communication event \> 0. However, there could be a situation that the contacts did not respond to the information, which lead to a failed activation. I adjust it as follows: a contact is activated if any of the two conditions is met:**                                                                                                                                                                                            |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     | Can you provide more thoughts on the results?                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | 1\) the communication event type is a Call;                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 2\) the communication event type is a message (SMS, MMS, or WhatsApp) and there are both '**outgoing**" and'**incoming**" messages (SMS, MMS, or WhatsApp).                                                                                                                                                                                                                                                                                                                                               |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | The above two conditions could ensure a **two-way communication (an effective activation)** exists between two smartphone users. This eliminates the possibility of one-way communication: one only sends or receives communication information. Overall, the estimation results are **mostly consistent with earlier results** after the adjustment.                                                                                                                                                     |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | ![](images/clipboard-2882367026.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 5   | It could be also interesting to explore how this effect vary by individual's perceived loneliness, their social interaction level, or maybe the timing of activation (e.g., morning vs night), etc.                                                                                                                                                                                                                                                                                                                                                                                                              | The third hypothesis is adjusted as follow:                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | An increase in communication with contacts with a high degree centrality improves the effectiveness of degree centrality in reducing smartphone usage.                                                                                                                                                                                                                                                                                                                                                    |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 6   | Smartphone addiction is measured by duration of smartphone use. But certain usages like seeking information or connecting can be productive. Why not consider defining addiction as screentime over a certain threshold?                                                                                                                                                                                                                                                                                                                                                                                         | Please refer to response 3.                                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 7   | "Activation" of a contact in a social media is determined by a single message or call. Shouldn't the frequency of interactions be considered? Would a weighted average make more sense here?                                                                                                                                                                                                                                                                                                                                                                                                                     | In robustness check, we adjust the activtion threshold as two-way communication. Please refer to response 4.                                                                                                                                                                                                                                                                                                                                                                                              |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 8   | In Figure 5, you handle missing contact information by referencing from the past or future. How often does such missing information happen? Wouldn't it be more appropriate to rely on the most recent survey only in order to capture the dynamic relationship?                                                                                                                                                                                                                                                                                                                                                 | We conducted a lookup operation to search for the missing contacts' social network information from the closest neighbors' social network surveys.                                                                                                                                                                                                                                                                                                                                                        |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | ![](images/search.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | We also conducted an alternative lookup approach by searching for the missing contacts backward first and then forward.                                                                                                                                                                                                                                                                                                                                                                                   |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | ![](images/search%20-%20bf-01.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                        |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | Both results are consistent with our original analysis:                                                                                                                                                                                                                                                                                                                                                                                                                                                   |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | ![](images/clipboard-2450557691.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 9   | Following the above point, how did you handle new relationships that emerged between biannual surveys?                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           | Please refer to response 8.                                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 10  | Figure 7 exemplifies social network activation. I'm curious about the repeated communications with a few out-of-network contacts: are these inbound or outbound? If these are mostly inbound with no response or occurred at regular times, it might be more reasonable to classify them as potential ads/promotions and exclude them from analysis.                                                                                                                                                                                                                                                             | 1.  Non-human contacts (promotions, advertising, fishing) are ruled out.                                                                                                                                                                                                                                                                                                                                                                                                                                  |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 2.  We conducted two-way activation threshold to ensure that activation of social network is successful.                                                                                                                                                                                                                                                                                                                                                                                                  |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 11  | Personality was included as a control. Shouldn't it remain consistent for an individual? If so, you should drop it from the fixed-effect model.                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | Personalities are measured based on social surveys so they could change over surveys. Due to the missing information for certain participants, we excluded the information for now.                                                                                                                                                                                                                                                                                                                       |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 12  | It's not necessary to write three functions for total, communication, and non-communication screen time; the model is the same.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | Thank you, it is corrected in the manuscript.                                                                                                                                                                                                                                                                                                                                                                                                                                                             |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 13  | Based on the \# observations, the unit of analysis seems to be person-week, but in your model and results, "t" indicates day. Please clarify.                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | Thank you, the structure of the data is individual \* day. However, time fixed effect is at the **week level** (**`studyweeks`**), even though our panel data is structured at potentially a more granular (daily) level with **`date`**                                                                                                                                                                                                                                                                  |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 14  | Your hypothesis 3 is about perceived loneliness but the results are missing.  What is the relationship between the perceived loneliness and one's actual communication pattern?                                                                                                                                                                                                                                                                                                                                                                                                                                  | The third hypothesis is adjusted as follow:                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | An increase in communication with contacts with a high degree centrality improves the effectiveness of degree centrality in reducing smartphone usage.                                                                                                                                                                                                                                                                                                                                                    |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

### 2025-01-06 posts/SP2 Review Response/ReviewResponse.qmd

| 15  | Please make the tables/figures self-explanatory. For example, in Table 6 it's unclear which column corresponds to which subsample. In Table 4, please specify the units for each variable.                                                                                                                                                                                                                                                                                                                                                                                                                       | Thank you, please refer to the manuscript for the recent correction in formats.                                                                                                                                                                                                                                                                                                                                                                                                                           |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

: Review Response for Dr.Jiayi Liu
:::
